%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\begin{document}

\introduction[
    fullname=Sayari Bhattacharya,
    email=sayaribhattacharya4@gmail.com,
    phone=+91 6294794677,
    linkedin=linkedin.com/in/sayari-bhattacharya-25b314219,
    %address=Kolkata{,}India
]

\summary{I specialize on Molecular Dynamics Simulations, which combine computational chemistry, biophysics, and data-driven approaches to investigate complex molecular behavior. My study focuses on exploring structural behaviour and aggregation pathway and mechanism of Intrinsically Disordered Proteins (IDPs) and their consequences in disease. I am committed to continuous learning and welcome exciting ideas outside of my field. My ultimate goal is to make a significant contribution to society and pushing the boundaries of knowledge, while embracing new concepts and methodologies along the way.}

\education{
    \educationItem[
        university=S.N. Bose National Centre for Basic Sciences{,} Kolkata{,} India-700106,
        college=3rd highest scorer in Class,
        graduation=June 2023,
        grade=grade 86\%,
        program=Master of Science{,} Physics,
        coursework= Atomic Molecular Physics{,} Advanced Quantum Mechanics{,} Computational Methods{,} Bio Physics{,} Statistical Mechanics{,} Mathematical Physics etc.
 ]\\
    \educationItem[university=Jadavpur University{,} Kolkata{,} India-700032,
        college= Among top 10 students in university,
        graduation=July 2021,
        grade= 81.67\% (CGPA : 8.77),
        program=Bachelor of Science{,} Physics(with Math and Chemistry minor),
        coursework=Classical Mechanics{,} Quantum Mechanics{,} Electrodynamics{,} Numerical methods etc.
]\\
    \Item[university=Chinsurah Balika Bani Mandir{,}Hooghly{,} India-712103,
        college= Among top 5 students in the state at 10th Board Examination\\
        Awarded "Best Student Award" in 2018.,
        graduation=June 2018,
        grade= grade 95.6\%,
        program=High School Diploma,
        coursework= Physics{,}Chemistry{,}Math{,}Computer Science{,}English.
 ]
}



\skills{
    \skillItem[
        category=Methods and Techniques,
        skills=Molecular Dynamics Simulation{,} Enhanced Sampling{,} Classical Nucleation Theory,
    ] \\
    \skillItem[
        category=Software and Modeling Tools,
        skills=Gromacs{,} VMD{,} PLUMED{,} Pymol{,}  Matplotlib{,} MDAnalysis,
    ] \\
    \skillItem[
        category=Programming,
        skills=Python{,}Fortran 95{,} Latex{,} C{,} C++(Basic Syntax),
    ]
}

\begin{workSection}{Experience}
    \experienceItem[
        company=S.N. Bose National Centre for Basic Sciences,
        location= Kolkata{,} West Bengal{,} India,
        position=Junior Research Fellow,
        duration= November 2023 – present
    ]
     \begin{itemize}
        \itemsep -6pt {} 
        \item Enhaced Sampling of diverse Conformational space of Intrinsically Disordered Protein(Amyloid oligomers) Enhanced Sampling Methods and Better CV desining. 
        \item Machine Learning based techniques to apply them in biological systems.
     \end{itemize}
     
\end{workSection}

\begin{workSection}{Academic projects}
     \customItem[
        title=Study of Nucleation for Crystallization from Solution,
        duration=September'2022 - December'2022,
        keyHighlight=Conducted comprehensive simulations on Silver nanoparticles and Supersaturated NaCl solutions{,} employing Molecular Dynamics techniques.
     ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Critically assessed the limitations of the Steinhardt's order parameter for crystalization{,} revealing valuable insights into phase transition.
        \item Characterized multistep nucleation processes, contributing to the understanding of crystallization kinetics and pathways.
        \item Effectively communicating findings through presentations and reports.
     \end{itemize}

     \customItem[
        title=Enhanced Sampling of Rare Events in MD Simulation,
        duration= January'2023 - May'2023,
        keyHighlight=Utilized Molecular Dynamics simulations to investigate stability of Amyloid fibril systems of varying oligomer lengths{,} focusing on rare event sampling.
     ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Employed Metadynamics to explore and sample free energy landscapes, providing deeper insights into the stability and aggregation mechanisms of Amyloid oligomers.
        \item Investigated critical length of an amyloid oligomer to be stable and how the Hydrogen bonds are contributing to the stability. Demonstrated proficiency in programming and computational tools.
     \end{itemize}
\end{workSection}

\begin{workSection}{Scholarships and Awards}
     \experienceItem[
        company= DST INSPIRE,
        location= Govt. of India,
        position=SHE Fellowship,
        duration=Dec 2018 – present
    ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Prestigious scholarship granted to the top 1\% of students nationwide persuing Basic Sciences based on 12th board examination performance.

     \end{itemize}

     \experienceItem[
        company=Jagadish Bose Natioal Science Talent Search,
        location=(JBNSTS),
        position= Senior Scholar,
        duration=October 2018 – Present
    ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Highly competitive award presented to the top 50 students within the state{,} achieved through a rigorous three-step selection process.
     \end{itemize}
     \experienceItem[
        company= Graduate Aptitude Test in Engineering,
        location=GATE-2023,
        position= Qualified,
        duration= March 2023– present
    ]
\end{workSection}

\begin{workSection}{Activities}
      \customItem[
        title= \bf{Sky Watching and Astronomy Camp},
        keyHighlight=Organized by JBNSTS and Sky Watcher's Association{,} Kolkata,
        duration=March 2019
    ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Learned optical telescope handling{,} indentifying stars in celestial sphere.
     \end{itemize}
     \customItem[
        title= \bf{'Vigyan Samagam' \\Organized by "Department of Science and Technology" and "Department of Atomic Energy"},
        keyHighlight= Dedicated Volunteer in science communication{,} actively contributed to public understanding of complex scientific concepts{,} with a focus on explaining the International Thermonuclear Experimental Reactor (ITER) project.,
        duration= December 2019
    ]
     \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {} 
        \item Adapting communication strategies to diverse age groups and backgrounds with the goal to educate people on the concepts, goals, and future possibilities of nuclear fusion research.
     \end{itemize}
\end{workSection}

\begin{workSection}{Hobbies}
    \begin{itemize}
        \vspace{-0.07em}
        \itemsep -6pt {} 
        \item Reading: Exploration of many genres, from scientific literature to fiction to horror, to broaden knowledge and creativity.
        \item Nature Photography: Enjoy immersing in nature capturing its beauty through photography.
     \end{itemize}
\end{workSection}
\end{document}